### 2014-08-08 tex/abstract.tex
Substantial edits to shorten introduction, etc.

      We show that the program {\sc flock} \citep{Duc&Tur2009} employs 
a model that is identical to the {\sc structure} 
\citep{Pritchardetal2000} model with no admixture and non-correlated 
allele frequency priors. The computational routine in {\sc flock} is 
formally equivalent to searching for the maximum-a-posteriori (MAP) 
estimate of this restricted {\sc structure} model via a simulated 
annealing algorithm with an extreme (and likely suboptimal) cooling 
schedule.  Understanding {\sc flock} as a special case of the model in 
{\sc structure} allows a principled perspective on its expected 
strengths and weaknesses.

>>>>

      We show that the the algorithm in the program {\sc flock} \citep{Duc&Tur2009} can be
interpreted as an estimation procedure using  
a model that is essentially identical to the {\sc structure} 
\citep{Pritchardetal2000} model with no admixture and non-correlated 
allele frequency priors. The computational routine in {\sc flock} is 
equivalent to searching for the maximum-{\em a-posteriori} (MAP) 
estimate of this restricted {\sc structure} model via a simulated 
annealing algorithm with an extreme cooling 
schedule (namely, the exponent on the objective function~$\rightarrow \infty$).  By analysis of a large, real data set we
confirm that {\sc flock} yields results similar to this restricted
{\sc structure} model, albeit with apparently more variability 
from run to run. Interpreting {\sc flock}'s algorithm as a special case of the model in 
{\sc structure} should aid in the understanding of the program's output and behavior.
